Digital Twins for Ocean Robots

### 2024-06-18 paper/paper.tex
mv docs/paper to paper (fix pdf build?)

\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:IndDispCode},
    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$. The repetition of `u` and `v` in `FlowFields` reflects that flow fields are treated as time invariant in this example.}
]
using IndividualDisplacements, DataFrames

@@

T=(0.,dT)
F=FlowFields(u,u,v,v,T)
I=Individuals(F,x,y)

[solve(I,T.+dT*(n-1)) for n in 1:nt]
trajectories=groupby(record(I),:ID)
\end{lstlisting}

>>>>

\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:IndDispCode},
    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$.}
]
using IndividualDisplacements

@@

T=(0.,dT)
F=FlowFields(u=u,v=v,period=T)
I=Individuals(F,x,y)

[solve!(I,T.+dT*(n-1)) for n in 1:nt]
trajectories=groupby(I,:ID)
\end{lstlisting}
